Higher-Order unification for free!

### 2024-04-11 paper/appendix.tex
link-beta -> link-llam

  type progress-beta-link-aux ho.tm -> ho.tm -> 
          ho.subst -> ho.subst -> links -> o.
  progress-beta-link-aux T1 T2 S1 S2 [] :-  is-in-pf T2, !,
    (T1 ==l T2) S1 S2.
  progress-beta-link-aux T1 T2 S S [@val-link-beta T1 T2] :- !.

  type progress-beta-link ho.tm -> ho.tm -> ho.subst -> 
        ho.subst -> links -> o.
  progress-beta-link T (ho.app[ho.uva V Scope | L] as T2) S S2 [@val-link-beta T T2] :- 
    arity T Arity, len L ArgsNb, ArgsNb >n Arity, !,
    minus ArgsNb Arity Diff, mem.new S V1 S1,
    eta-expand (ho.uva V1 Scope) Diff T1,
    ((ho.uva V Scope) ==l T1) S1 S2.

  progress-beta-link (ho.uva _ _ as T) (ho.app[ho.uva Ad1 Scope1 | L1] as T1) S1 S3 NewLinks :-
    append Scope1 L1 Scope1L,
    pattern-fragment-prefix Scope1L Scope2 L2,
    not (Scope1 = Scope2), !,
    mem.new S1 Ad2 S2,
    len Scope1 Scope1Len,
    len Scope2 Scope2Len,
    make-eta-link Scope1Len Scope2Len Ad1 Ad2 [] LinkEta S2 S3,
    if (L2 = []) (NewLinks = LinkEta, T2 = ho.uva Ad2 Scope2) 
      (T2 = ho.app [ho.uva Ad2 Scope2 | L2], 
      NewLinks = [@val-link-beta T T2 | LinkEta]).

@@

  progress-beta-link T1 (ho.app[ho.uva _ _ | _] as T2) H H [@val-link-beta T1 T2] :- !.

@@

  solve-link-abs (@val-link-beta A B) NewLinks S S1 :- !,
    progress-beta-link A B S S1 NewLinks.

@@

  type commit-links-aux link -> ho.subst -> ho.subst -> o.
  commit-links-aux (@val-link-eta T1 T2) H1 H2 :- 
    ho.deref H1 T1 T1', ho.deref H1 T2 T2',
    (T1' ==l T2') H1 H2.
  commit-links-aux (@val-link-beta T1 T2) H1 H2 :- 
    ho.deref H1 T1 T1', ho.deref H1 T2 T2',
    (T1' ==l T2') H1 H2.
  commit-links-aux (ho.abs B) H H1 :- 
    pi x\ commit-links-aux (B x) H H1.

>>>>

  type progress-beta-link-aux ho.tm -> ho.tm -> 
          ho.subst -> ho.subst -> links -> o.
  progress-beta-link-aux T1 T2 S1 S2 [] :-  is-in-pf T2, !,
    (T1 ==l T2) S1 S2.
  progress-beta-link-aux T1 T2 S S [@val-link-llam T1 T2] :- !.

  type progress-beta-link ho.tm -> ho.tm -> ho.subst -> 
        ho.subst -> links -> o.
  progress-beta-link T (ho.app[ho.uva V Scope | L] as T2) S S2 [@val-link-llam T T2] :- 
    arity T Arity, len L ArgsNb, ArgsNb >n Arity, !,
    minus ArgsNb Arity Diff, mem.new S V1 S1,
    eta-expand (ho.uva V1 Scope) Diff T1,
    ((ho.uva V Scope) ==l T1) S1 S2.

  progress-beta-link (ho.uva _ _ as T) (ho.app[ho.uva Ad1 Scope1 | L1] as T1) S1 S3 NewLinks :-
    append Scope1 L1 Scope1L,
    pattern-fragment-prefix Scope1L Scope2 L2,
    not (Scope1 = Scope2), !,
    mem.new S1 Ad2 S2,
    len Scope1 Scope1Len,
    len Scope2 Scope2Len,
    make-eta-link Scope1Len Scope2Len Ad1 Ad2 [] LinkEta S2 S3,
    if (L2 = []) (NewLinks = LinkEta, T2 = ho.uva Ad2 Scope2) 
      (T2 = ho.app [ho.uva Ad2 Scope2 | L2], 
      NewLinks = [@val-link-llam T T2 | LinkEta]).

@@

  progress-beta-link T1 (ho.app[ho.uva _ _ | _] as T2) H H [@val-link-llam T1 T2] :- !.

@@

  solve-link-abs (@val-link-llam A B) NewLinks S S1 :- !,
    progress-beta-link A B S S1 NewLinks.

@@

  type commit-links-aux link -> ho.subst -> ho.subst -> o.
  commit-links-aux (@val-link-eta T1 T2) H1 H2 :- 
    ho.deref H1 T1 T1', ho.deref H1 T2 T2',
    (T1' ==l T2') H1 H2.
  commit-links-aux (@val-link-llam T1 T2) H1 H2 :- 
    ho.deref H1 T1 T1', ho.deref H1 T2 T2',
    (T1' ==l T2') H1 H2.
  commit-links-aux (ho.abs B) H H1 :- 
    pi x\ commit-links-aux (B x) H H1.
